DraftOne

### 2016-06-22 DraftOne.Rmd
Finishing script files

This is the percent of all estimated coefficients for the $n$ simulations where the lower 95% confidence interval is above 0 [@figueiras2005analysis]. This is a metric of statistical efficiency.

@@

```{r}
# Measure power
power_beta <- function(df){
        no_zero <- df$lower_ci >= 0 | df$upper_ci <= 0
        out <- data.frame(power = sum(no_zero) / nrow(df))
        return(out)
}

@@

```{r}
check_sims <- function(df, true_rr){
        a <- mean_beta(df)
        b <- beta_var(df)
        c <- beta_bias(df, true_rr = true_rr)
        d <- coverage_beta(df, true_rr = true_rr)
        e <- power_beta(df)

        out <- cbind(a, b, c, d, e)
        return(out)
}
check_sims(rep_df, true_rr = 1.02)
```

@@

```{r}
power_calc <- function(varying, values, plot = FALSE, ...){
        out <- data.frame(x = values, power = NA)
        if(varying == "n"){
                for(i in 1:nrow(out)){
                        rep_df <- rep_sims(n = out$x[i], ...)
                        out$power[i] <- power_beta(rep_df)[1,1]
                }
        } else if(varying == "rr"){
                for(i in 1:nrow(out)){
                        rep_df <- rep_sims(rr = out$x[i], ...)
                        out$power[i] <- power_beta(rep_df)[1,1]
                }
        } else if(varying == "lambda"){
                for(i in 1:nrow(out)){
                        rep_df <- rep_sims(lambda = out$x[i], ...)
                        out$power[i] <- power_beta(rep_df)[1,1]
                }
        }

        if(plot == TRUE){
                        library(ggplot2)
                        my_plot <- ggplot(out, aes(x = x, y = power)) + 
                                geom_line() + theme_minimal() + 
                                xlab(varying)
                        print(my_plot)
        }

        colnames(out)[1] <- varying
        return(out)
}
```

>>>>

This is the percent of all estimated coefficients for the $n$ simulations where the lower 95% confidence interval bound is above 0 [@figueiras2005analysis]. This is a metric of statistical efficiency.

@@

```{r}
# Measure power
power_beta

@@

```{r}
check_sims 
check_sims(rep_df, true_rr = 1.02)
```

@@

```{r}
power_calc 
```
